SST_patterns

### 2019-09-08 SST_patterns.Rmd
updated

# You may then use the 'pixel_match' object to filter out the desired pixels from the full satellite products
temp_match <- function(df){
  temp <- df %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  filter(combi %in% pixel_match$combi)
}

>>>>

# You may then use the 'pixel_match' object to filter out the desired pixels from the full satellite products
temp_match <- function(df){
  temp <- df %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  filter(combi %in% pixel_match$combi) %>% 
  select(distance)
}
